### 2023-12-10 sections/2-methods.tex
added deltas image
fix to Sieve

Given a Cluster $C$, let $c$ be its center and $r$ be its radius. Our $\rho$- and $k$-NN algorithms make use of the following properties:

@@

In this algorithm, we perform $\rho$-nearest neighbors search starting with a small search radius, and repeatedly increasing the radius until we find $k$ neighbors.

@@

In this algorithm, we begin by letting $Q$ be a list of clusters and points, starting with only the root cluster. 
While $Q$ contains at least one cluster (i.e., $Q$ is not a list of only points), we repeat the process described in 
the following paragraphs.

@@

\begin{algorithm} % enter the algorithm environment
    \caption{Sieve(\emph{root, query, k})} % give the algorithm a caption
    \label{alg:methods:sieve} % and a label for \ref{} commands later in the document
    \begin{algorithmic} % enter the algorithmic environment
        \REQUIRE $root$, $query$, $k$
        \REQUIRE $root.cardinality \geq k$
        \STATE $Q \Leftarrow$ [$root$]
        \WHILE{$|Q| > k$}
            \STATE $i \Leftarrow QuicksortPartition(Q, k)$
            \STATE $\tau \Leftarrow Q[i].\delta_{max}$
            \FOR {$q \in Q$}
                \IF {$q.\delta_{min} > \tau$}
                    \STATE $Q.pop(q)$
                \ENDIF
            \ENDFOR
            \FOR {$q \in Q$}
                \IF {$q.isLeaf \lor |q| \leq k$}
                    \STATE $Q.append(q.points)$
                \ELSE
                    \STATE $[l, r] \Leftarrow q.children$
                    \STATE $Q.append([l, r])$   
                \ENDIF
                \STATE $Q.remove(q)$
            \ENDFOR 
        \ENDWHILE
        \STATE Return $Q$
    \end{algorithmic}How do we algorithmically determine the depth to which we
\end{algorithm}

\subsubsection{Sieve with Separate Centers}
\label{subsubsec:methods:knn-search:sieve2}

This algorithm is the same as Sieve, but with the following modification:
clusters in $Q$ are represented twice -- once as their center and once as the rest of their points.
The clusters' multiplicities in $Q$ are adjusted to be one less than their cardinalities.
Because we have that for any cluster $C$, $C.\delta \leq C.\delta_{max}$, representing the cluster center separately from the rest of the points causes the threshold $\tau$ to decrease more quickly, thus allowing us to eliminate some clusters from $Q$ earlier in the process.

>>>>

\begin{figure}[ht!]
    \centering
    \includegraphics[scale=0.5]{images/geometry/deltas.png}
    \caption{}
    \label{fig:methods:deltas}
\end{figure}

Given a Cluster $C$, let $c$ be its center and $r$ be its radius. Our $\rho$- and $k$-NN algorithms make use of the following properties, as illustrated in Figure~\ref{fig:methods:deltas}.

@@

In this algorithm, we perform $\rho$-nearest neighbors search starting with a small search radius,
\subsubsection{Sieve with Separate Centers}
\label{subsubsec:methods:knn-search:sieve2}

This algorithm is the same as Sieve, but with the following modification:
clusters in $Q$ are represented twice -- once as their center and once as the rest of their points.
The clusters' multiplicities in $Q$ are adjusted to be one less than their cardinalities.
Because we have that for any cluster $C$, $C.\delta \leq C.\delta_{max}$, representing the cluster center separately from the rest of the points causes the threshold $\tau$ to decrease more quickly, thus allowing us to eliminate some clusters from $Q$ earlier in the process.  and repeatedly increasing the radius until we find $k$ neighbors.

@@

In this algorithm, we begin by letting $Q$ be a list of clusters and points. 
{ \color{red} We represent each cluster twice in $Q$ -- once as just its center and once as the rest of its points. $Q$ is initialized with two elements: the root cluster and the root cluster's center. }

While $Q$ contains at least one cluster (i.e., $Q$ is not a list of only points), we repeat the process described in 
the following paragraphs.

@@

\begin{algorithm} % enter the algorithm environment
    \caption{Sieve(\emph{root, query, k})} % give the algorithm a caption
    \label{alg:methods:sieve} % and a label for \ref{} commands later in the document
    \begin{algorithmic} % enter the algorithmic environment
        \REQUIRE $root$, $query$, $k$
        \REQUIRE $root.cardinality \geq k$
        \STATE $Q \Leftarrow$ [$root$]
        \WHILE{$|Q| > k$}
            \STATE $i \Leftarrow QuicksortPartition(Q, k)$
            \STATE $\tau \Leftarrow Q[i].\delta_{max}$
            \FOR {$q \in Q$}
                \IF {$q.\delta_{min} > \tau$}
                    \STATE $Q.pop(q)$
                \ENDIF
            \ENDFOR
            \FOR {$q \in Q$}
                \IF {$q.isLeaf \lor |q| \leq k$}
                    \STATE $Q.append(q.points)$
                \ELSE
                    \STATE $[l, r] \Leftarrow q.children$
                    \STATE $Q.append([l, r])$   
                \ENDIF
                \STATE $Q.remove(q)$
            \ENDFOR 
        \ENDWHILE
        \STATE Return $Q$
    \end{algorithmic}
\end{algorithm}
